A Standard for the Scholarly Citation of Archaeological Data

### 2017-09-06 analysis/paper/paper.Rmd
upload tdar DOIs to osf

@@

# It doesn't get much of tDAR, so let's be more specific 
# dc_arch_tdar <- dc_search(q = "10.6067", rows = pretty(100000)[2])

@@

# Download from osf.io with this:
# library(osfr)
# download_file("tsm89", private = TRUE)
dc_arch <- readRDS("../data/raw_data/dc_arch.rds")
dc_arch_tdar <- readRDS("../data/raw_data/dc_arch_tdar.rds")
dc_arch <- bind_rows(dc_arch, dc_arch_tdar)
```

>>>>

# osf project is at https://osf.io/ksruz/

@@

# It doesn't get much of tDAR, so let's be more specific 
# dc_arch_tdar <- dc_search(q = "10.6067", rows = pretty(100000)[2])
# library(osfr)
# upload_file("ksruz", "analysis/data/raw_data/dc_arch_tdar.rds", dest = "dc_arch_tdar.rds")

@@

# Download from osf.io with this:
# library(osfr)
# download_file("tsm89", private = TRUE)

dc_arch <- readRDS("../data/raw_data/dc_arch.rds")
dc_arch_tdar <- readRDS("../data/raw_data/dc_arch_tdar.rds")
dc_arch <- bind_rows(dc_arch, dc_arch_tdar)
```
